---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CUInetwork

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of CUInetwork is to ...

## Installation

To install the latest development version from GitHub:

``` r
install.packages("remotes")
remotes::install_github("xinxiong0238/CUInetwork")
```
If errors like "Error: (converted from warning) package 'shiny' was built under R version 4.0.5" occur, please set:

``` r
Sys.setenv("R_REMOTES_NO_ERRORS_FROM_WARNINGS" = "true")
```
You can refer to [this website](https://github.com/r-lib/remotes/issues/403) to see more discussion on that problem.


## Example

This is a basic example which shows you how to run the CUInetwork app. Remember you need to get access to the data and save it to your local computer. Remember in order to guarantee some dependencies are loaded, you must use `library(CUInetwork)` beforehand, instead of directly running CUInetwork::run_app(data_path)!

```{r example}

library(CUInetwork)


# data_path = "the path to the app data (RDS format)"
# run_app(data_path)
```
